---
title: 'DS 202:  Final Project Code'
author: "Jaden Birkner"
date: "12/7/2019"
output: html_document
---

#Jaden
```{r}
library(tidyverse)
library(tidyr)
```


```{r}
nycdf = read.csv("nycdata.csv")
names(nycdf) <- tolower(names(nycdf))
head(nycdf)
```

```{r}
str(nycdf)
```

Cleaning data for analysis of boroughs.

```{r}
nyc = filter(nycdf, boro != 0)
nyc = drop_na(nyc)
str(nyc)
```

```{r}
filter(nyc, boro == 0)
```

Exploring distribution of restaurants across boroughs.

```{r}
ggplot(nyc, aes(x=boro)) + geom_bar()
```

Cleaning data for analysis of grade distribution across boroughs.

```{r}
nyc2 = filter(nyc, grade != "")
length(nyc2$grade)
```

Visualizing distribution of grades across boroughs.

```{r}
ggplot(nyc2, aes(x=boro)) + geom_bar(aes(fill=grade), position = "fill")
```

#Alex

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##data load
data = read.csv("nycdata.csv")
library(knitr)
data[data==""] = NA
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

Displaying the levels of Violation Codes and Inspection Types.

```{r echo=FALSE}
summary(data[,"VIOLATION.CODE"])
```

```{r include=FALSE}
violationCode = group_by(data, VIOLATION.CODE)
```

Information about each code, with average score, and modes

```{r echo=FALSE}
kable(head(arrange(summarise(violationCode, SCORE = mean(SCORE), CUISINE.DESCRIPTION = getmode(CUISINE.DESCRIPTION), BORO = getmode(BORO), INSPECTION.TYPE = getmode(INSPECTION.TYPE)),SCORE),20))
```

```{r include=FALSE}
freq = data.frame(table(violationCode[,"VIOLATION.CODE"]) )
names(freq) = c("ViolationCode", "Frequency")
```

Visualization of most frequent violation codes

```{r echo=FALSE}
freq = arrange(freq, -Frequency)
ggplot(freq[1:10,],aes(x=ViolationCode, y=Frequency, color = ViolationCode)) + geom_point(aes(size = 2)) + guides(color=FALSE, n=FALSE, size = FALSE) + labs(x="Violation Code", title="Frequency of Top 10 Violation Codes")
```

#Mikaela

Cuisine description.

```{r}
library(leaflet)
library(leaflet.extras)
library(ggmap)
```

```{r}
table(nyc$INSPECTION.DATE)
```


```{r}
nyc <- read.csv("nycdata.csv")
```

Col Names for quick reference
```{r}
names(nyc)
str(nyc)
```

```{r}
length(table(nyc$CUISINE.DESCRIPTION))

table(nyc$CRITICAL.FLAG)
```

Restaurants that did not have a correct input were labeled as 0 so we are removing them.
```{r}
nyc = nyc %>%
  filter(BORO != '0')

```


```{r}
nycFlag = nyc %>%
  filter(CRITICAL.FLAG == "Y") %>%
  group_by(BORO) 
  
table(nycFlag$BORO)
table(nyc$BORO)

table(nycFlag$BORO)/table(nyc$BORO)

```


```{r}
#table(nyc$CUISINE.DESCRIPTION)
#table(nyc$CUISINE.DESCRIPTION[nyc$SCORE>=7])/table(nyc$CUISINE.DESCRIPTION)
table(nyc$CUISINE.DESCRIPTION[nyc$CRITICAL.FLAG=="Y"])/table(nyc$CUISINE.DESCRIPTION)
#top10 = table(nyc$CUISINE.DESCRIPTION[nyc$SCORE>=12])/table(nyc$CUISINE.DESCRIPTION)
```


```{r}
nyc %>%
  group_by(CUISINE.DESCRIPTION) %>%
  tally(SCORE) %>%
  top_n(10)

nyc %>%
  group_by(CUISINE.DESCRIPTION) %>%
  tally(length(CUISINE.DESCRIPTION)) %>%
  arrange(desc(n)) %>%
  top_n(10)
```

```{r}
nyc %>%
  group_by(CUISINE.DESCRIPTION) %>%
  tally(SCORE/length(CUISINE.DESCRIPTION)) %>%
  arrange(desc(n)) %>%
  top_n(10)

```


```{r}
bangladeshi = nyc %>%
  filter(CUISINE.DESCRIPTION == "Bangladeshi")

boxplot(bangladeshi$SCORE,horizontal = TRUE)
mean(bangladeshi$SCORE,na.rm = TRUE)
median(bangladeshi$SCORE,na.rm = TRUE)
```


```{r}
nyc %>%
  group_by(DBA) %>%
  tally(length(DBA)) %>%
  top_n(10) %>%
  arrange(desc(n))

length(nyc$DBA[nyc$DBA=="GOLDEN KRUST CARIBBEAN BAKERY & GRILL"])
```


```{r}
nycChain = nyc %>%
  unite("address",c("BUILDING","STREET"))
```


```{r}
nycChain %>%
  group_by(DBA) %>%
  tally(SCORE/length(DBA)) %>%
  arrange(desc(n)) %>%
  top_n(10)
```

```{r}
nycCAMIS = nyc %>%
  group_by(DBA) %>%
  filter(!duplicated(CAMIS))

length(nycCAMIS$DBA=="SUBWAY")
```


```{r}
nycBrosFM = nycChain %>%
  filter(DBA == "BROTHERS FISH MARKET")


leaflet(data = nycBrosFM) %>%
      addTiles(
        urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>%
      addMarkers(lat = ~Latitude, lng = ~Longitude)

```



```{r}
nyc %>%
  group_by(CAMIS) %>%
  filter(!is.na(SCORE)) %>%
  mutate(totalScore = sum(SCORE)) %>%
  filter(!duplicated(CAMIS)) %>%
  group_by(CUISINE.DESCRIPTION) %>%
  summarise(avgScore = sum(totalScore)/length(CAMIS)) %>%
  arrange(desc(avgScore))


```



```{r}
nycB = nyc %>%
  filter(!is.na(SCORE)) %>%
  filter(CUISINE.DESCRIPTION == "Bangladeshi") %>%
  group_by(CAMIS) %>%
  mutate(totalScore = sum(SCORE)) %>%
  filter(!duplicated(CAMIS))
  

nycB
```



```{r}
leaflet(data = nycB) %>%
      addTiles(
        urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>%
      addMarkers(lat = ~Latitude, lng = ~Longitude)
```

https://rstudio.github.io/leaflet/
```{r}
pal <- colorNumeric(
   palette = "Reds",
  domain = nycB$totalScore)

 leaflet(data = nycB) %>%
      addTiles(
        urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>') %>%
      addCircleMarkers(color = ~pal(nycB$totalScore), opacity = 1) %>%
     addLegend("bottomright", pal = pal, values = ~nycB$totalScore,
    title = "Score By Restaurant",
    labFormat = labelFormat(prefix = ""),
    opacity = 1
  ) %>%
      addSearchOSM() %>%
      addResetMapButton()

```

